How economic, health and social factors affect life expectancy in developing countries?

### 2025-04-10 paper.Rmd
fixed caption

plot(secondary_model_infant_lg, which = 1)
hist(rstandard(secondary_model_infant_lg))
```
Our preliminary model violated the assumptions of linearity and constant variance. There was also a minor violation of the normal errors assumption as they were slightly skewed left. However, post adding the log transformations, the improved model does not violate these assumptions.

>>>>

plot(secondary_model_infant_lg, which = 1)
hist(rstandard(secondary_model_infant_lg),  main="Histogram of Standized Residuals", xlab="Residuals")
```
Our preliminary model violated the assumptions of linearity and constant variance. There was also a minor violation of the normal errors assumption as they were slightly skewed left. However, post adding the log transformations, the improved model does not violate these assumptions.
